---
title: "Documentation"
author: "ESA99"
format: html
theme: darkly
---

```{r}
#| echo: false
#| message: false

library(terra)
library(sf)
library(tmap)
library(dandelion)

```


## TODO

 - (Re-)run final predictions of all groups (including % difference now)
 - Create different kind of plots/visuallization types for the results
    - play around with it
    - change axis
    - try different colours
 - Implementation of lat/long (evtl. as HiWi)
 - Comparison: get exactly the original data for the input (Switzerland demo tile?)
    - rerun the prediction and compare to original prediction
      - How much is normal difference by CNN prediction, what is actually a difference by the prediciton or code?
  - Texture manipulation
      - flip, rotate
      - smooth, contrast up/down

## Status

The current code is setup to calculate averages, absolute value avergaes, percentage deviations and standard deviation. But not all difference-raster values are saved for storage reasons.


### Tiles used for deployment


```{r}
#| echo: false
#| message: false

selected_tiles <- st_read("/home/emilio/canopy_height/R/data/final_tile_selection.gpkg")

tmap::tmap_mode("view")
tmap::tm_shape(selected_tiles) +
  tmap::tm_borders(col = "red", lwd = 2) +
  tmap::tm_text("Name", size = 0.8, col = "black")+
  tmap::tm_view(
                basemaps = c("Esri.WorldImagery", "OpenStreetMap"),
                set.view = c(10.0, 20.0, 2))  # longitude, latitude, zoom level
```


## Deployment

To run the model use the following code inside the terminal. Beforehand set all the variables inside the script `deploy.R` and make sure all image folders are in the correct place and named correctly (Tile name without "T": "49UCP").

``` bash

conda activate gchm
cd /home/emilio/canopy_height/
Rscript deploy.R
```

## Lat/Long findings

Location has a big impact on the prediction. - North-South gradient - Continentality - whatch out for oceans when linking the projects or calculating lat long - specific lat/long values vs. difference to original location - method "comparison" -\> which is better for analysis/presentation

## Technical learnings

This code sets up to treat (for example gchm) a folder as a python package after looking for setup.py

``` bash
pip install -e .
```

## Quarto

```{r}
#| echo: false
2 * 2
```
